\section{Motivation for Cohomology}
One of the most important invariants of schemes is \'etale cohomology.  Cohomology is an important invariant in geometry and topology which associates to each space $X$ a sequence of abelian groups $H^i(X)$, $i \ge 0$, the cohomology groups of $X$. For each map $f: X \to Y$ of spaces there are homomorphisms $f^*: H^i(Y) \to H^i(X)$. Moreover there are so called coboundary morphisms $\partial^i : H^i \to H^{i+1}$ for each $i \ge 0$.
\begin{definition}
	A \textit{cohomology theory} for
\end{definition}
We can deduce many interesting properties of spaces from their cohomology groups and the associated homomorphisms.

An important and intuitive cohomology is \textit{singular cohomology}. It provides a rigorous way for counting ``holes'' in a topological space. For instance, the circle $S^1$ has 1 one-dimensional hole while the torus $T^2$ has 2. The sphere $S^2$ has 1 two-dimensional hole but no one-dimensional holes, in symbols\footnote{$\Z$ appears here because it is the free group on one generator.}
\begin{align*}
	H^1_{sing}(S^1) \simeq \Z,\quad & H^1_{sing}(T^2) \simeq \Z \oplus \Z, \\
	H^1_{sing}(S^2) \simeq  0,\quad & H^2_{sing}(S^2) \simeq \Z.
\end{align*}
A general approach to cohomology is to use sheaves on a topological space as ``coefficients''. Sheaves consist of local data on a space that is glueable. A basic example consists of functions on a space: If we have an open cover $\{ U_i\}$ for a manifold $M$ and functions $f_i: M \to \R$ that agree on all intersections $U_i \cap U_j$ we may patch it together to a function $f: M \to \R$.
For any space $X$ and any sheaf $\Sh{F}$ on $X$ we can define $H^i(X, \Sh{F})$. Many examples of cohomology theories turn out to stem from the cohomology of a particular sheaf. For example, if $X$ is a locally contractible space, the singular cohomology $H_{\text{sing}}^i(X)$ of $X$ is isomorphic to the sheaf cohomology $H^i(X, \Z_X)$ of the constant sheaf $\Z_X$ on $X$.

One of the main motivations for \'etale cohomology is that one would like a replacment for singular cohomology for schemes. There are a number of obstacles:
\begin{proposition}\label{scheme_contractible}
	An irreducible scheme is contractible.
\end{proposition}
\begin{proof}
	Define a map $f: X \times I \to X$  by $f(x,0) = x$ and $f(x,t) = \eta$ for $t > 0$. This is a contraction of $X$ onto the point $\eta$, so the singular cohomology of $X$ is identically 0.
\end{proof}

\begin{proposition}
	$H^i(X, \Sh{F})$ is 0 for any sheaf on an irreducible topological space.
\end{proposition}
\begin{proof}
	See section TODO.
\end{proof}
This is a strong indication that the traditional tools of cohomology are inadequate to analyse the geometry of schemes.


\section{Fundamental groups}
Another important invariant of spaces is the fundamental group. The fundamental group of a pointed topological space $(X,x)$, denoted by $\pi_1(X,x)$ may be defined in two equivalent ways: Via homotopy classes of loops in $X$ based at $x$, or as the automorphism group of the fiber functor $F_x: Cov(X) \to Set$. From the first perspective, the fundamental group measures the connectivity of a space. The construction makes use of the unit interval. The unit interval $[0,1] \subset \R$ is not an algebraic set so the first definition does not have a natural formulation using only the notions of algebraic geometry. The second approach yields a theory strongly reminiscent of Galois theory. Grothendieck pioneered this approach in algebraic geometry.

\subsection{The fundamental group via paths}
A loop with base point $x$ is a map $\gamma : [0,1] \to X$ such that $\gamma(0) = \gamma(1) = x$. The homotopy class of $\gamma $ is denoted by $[\gamma]$. Define a composition operation by concatenation: $[\gamma] \circ [\eta] = [\gamma \circ \eta]$, where $\gamma \circ \eta$ is defined to be the path
\[
	\gamma \circ \eta =
	\begin{cases}
		\ \eta(2x) \text{ for } x \in [0, \tfrac{1}{2}] \\
		\ \gamma(2x - 1) \text{ for } x \in [\tfrac{1}{2}, 1].
	\end{cases}
\]
It is clear that this construction yields a group structure on the set
\[
	\{\ [\gamma] \mid \gamma : [0,1] \to X , \gamma(0) = \gamma(1) = x \}
\]
of homotopy classes of loops at $x$.

\subsection{The monodromy action}

\begin{construction}[Covering spaces]
	Let $X$ be a topological space. A \textit{space over $X$ } is a topological space $Y$ together with a continuous map $Y \to X$. A morphis between two spaces $Y_1, Y_2$ over $X$ is a continuous map $f: Y_1 \to Y_2$ such that the diagram
	\[
		% https://q.uiver.app/?q=WzAsMyxbMCwwLCJZXzEiXSxbMiwwLCJZXzEiXSxbMSwxLCJYIl0sWzAsMSwiZiJdLFsxLDIsInBfMiJdLFswLDIsInBfMSIsMl1d
		\begin{tikzcd}
			{Y_1} && {Y_1} \\
			& X
			\arrow["f", from=1-1, to=1-3]
			\arrow["{p_2}", from=1-3, to=2-2]
			\arrow["{p_1}"', from=1-1, to=2-2]
		\end{tikzcd}
	\]
	commutes. We obtain the category $\Top/X$ of spaces over $X$. A space $f: Y \to X$ over $X$ is called a local homeomorphism if for any point $y \in Y$ there is a neighborhood $U$ of $x$ such that the preimage $f^{-1}(U)$ is homeomorphic to a disjoint union of the open sets $f^{-1}(U) \cong \coprod U_i$ such that each $U_i$ gets mapped to $U$ homeomorphically under $f|_{U_i}$. Surjective local homeomorphisms over a space $X$ are also called \textit{covering spaces of $X$} or simply \textit{coverings}. Let $f: Y \to X$ be a surjective local homeomorphism. A trivial covering is one of the form $p: \coprod X \to X$, where $p$ restricts to the identity on each component. Using this terminology one can also say that a covering is a \textit{locally trivial local homemorphism}.
\end{construction}

\begin{lemma}[Path-lifting property of covering spaces]
	Let $p: Y \to X$ be a cover, $y \in Y$ and $x = p(y) \in X$.
	\begin{enumerate}
		\item If $f: [0,1] \to X$ is a path in $X$ with $f(0) = x$, then there is a unique path $\tilde{f}: [0,1] \to Y$ with $\tilde{f}(0) = y$ and $p \circ \tilde{f} = f$
		\item Assume we have a second path $g \colon [0,1] \to X$ homotopic to $f$ with the same endpoints. Then the unique lift $\tilde{g}$ of $g$ to $Y$ is homotopic to $\tilde{f}$ with the same endpoints.
	\end{enumerate}
\end{lemma}

\begin{proof}
	See \cite{Szamuely}, Lemma 2.3.2.
\end{proof}

\begin{construction}[The monodromy action]
	Let $p(y)=x$ and let $\alpha \in \pi_1(X,x)$ be represented by a path $f: [0,1] \to X$. By the previous lemma, there is a unique lift $\tilde{f}$ with $\tilde{f}(0) = y$. Since $p \circ \tilde{f} = f$, we have $(p \circ \tilde{f})(1) = x$, so the fundamental group $\pi_1(X, x)$ acts on $F_x(Y)$. This action is called the \textit{monodromy action}.
\end{construction}

A $Y$-automorphism is defined to be an automorphism of $Y$ in $\Top/X$. Let $Cov(X)$ be the subcategory of $\Top/X$ consisting of covering spaces. For each point $x \in X$ there is a functor $F_x: Cov(X) \to \Set$, sending a covering $p: Y \to X$ to the set $\{y \in Y \mid p(y) = x\}$. Now define an automorphism of $F_x$ to be a natural transformation $\psi: F_x \to F_x$ with a two-sided inverse. The set $\text{Aut}(F_x)$ of automorphisms of $F_x$ carries the structure of a group by composition. Note that for a covering $Y$ of $X$ and an automorphism $\phi \in \text{Aut}(F_x)$, there is by definition a morphism $\phi(Y): F_x(Y) \to F_x(Y)$. We define $\pi_1(X,x)$ to be the automorphism group of $F_x$.

We would like to have a notion of fundamental group for schemes. As before, there are some obstacles:

\begin{itemize}
	\item As we have seen in~\ref{scheme_contractible}, any irreducible scheme $X$ is contractible. As every loop in an irreducible scheme is contractible, this implies that $\pi_1(X)$ is $0$. In a sense this means that the unit interval is not a suitable ``test space'' to probe varieties and schemes.
	\item There is no universal covering space.
	      For instance, the algebra homomorphism given by $x^n \to x^n, k[x^n] \to k[x]$ corresponds to a map $x \to x^n, \mathbb{A}^1_k \to \mathbb{A}^1_k$. Depicted is the map from $\mathbb{A}^1_\C$ to $\mathbb{A}^1_\C$ for the case $n=2$

	      %\input{chapters/introduction/logarithm.tex}

	      This map \textit{should} be local homeomorphism, but this is false in the Zariski topology. There do not exist nonempty open subsets $V$ and $U$ such that $x \to x^n$ maps $V$ isomorphically onto $U$. The theory of \'etale coverings will give us a good notion of covering which we will use to define the analog of universal coverings
\end{itemize}

The \'etale topology will provide a solution for the problems we have with both cohomology and fundamental groups. The \'etale topology is not a topology in the classical sense, but a category equipped with a notion of covering (in the sense of point-set topology). The analog of open sets of a scheme $X$ will be so called \'etale morphisms $U \to X$. \'Etale morphisms are the natural analogs of local homeomorphisms in scheme theory, so they provide a finer topology than the Zarisiki topology, giving rise to a better sheaf theory. Furthermore, surjective \'etale morphisms share a lot of formal properties with covering spaces, allowing us to define the \'etale fundamental group $\pi_1^{\et}$.
\section{Galois cohomology}
The simplest case of \'etale cohomology is the case of fields. In this case, \'etale cohomology is equivalent to Galois cohomology.
Let $M$ be a $G$ module for $G$ a finite group, meaning that $M$ is an abelian group with a left $G$-action. We will later also consider profinite groups because we are interested in the case of absolute Galois groups. A $G$-module homomorphism is a $G$-equivariant homomorphism. Denote by $M^G = \{m \in M \mid gm = g, \ \forall g \in G\}$ the submodule of $G$-fixed points.
\begin{example}
	Let $G = \Gal(L/k)$. We have the following examples:
	\begin{itemize}
		\item By Galois theory the fixed field of $L$ under $G$ is exactly $L^G = k$
		\item $\mathcal{O}_L^G = \mathcal{O}_k$.
		\item $\mu_n(L)^G = \mu_n(k)$
	\end{itemize}
\end{example}

Let $P, M$, and $N$ be $G$-modules fitting into an exact sequence
\[
	0 \to P \xrightarrow{\alpha} M \xrightarrow{\beta} N \to 0
\]
and let
\[
	P^G \xrightarrow{\alpha'} M^G \xrightarrow{\beta'} N^G
\]
be the resulting sequence. The map $\alpha'$ is just the restriction of an injective map, so $\alpha$ is injective.
Note:
$\ker(\beta') = \ker \beta \cap M^G$

We will show that $im(\alpha') = im(\alpha) \cap M^G$.
Note that $im(\alpha') \subset im(\alpha) \cap M^G$.
For the other inclusion let $m \in im(\alpha) \cap m^G$. There exists a $p \in P$ such that $\alpha(p)=m$. Now let $\sigma \in G,\ \sigma(\alpha(p)) = \sigma(m) = m$,
Since $\alpha(\sigma(p)) = \alpha(p) = m$ and $\alpha$ is injective, $p = \sigma(p)$ so $p$ is fixed under the $G$-action. $im(\alpha) = \ker(\beta) \implies im(\alpha) \cap M^G = \ker(\beta) \cap M^G$.
However, the functor is not right exact:
\begin{example}
	\[1 \to \{\pm 1\} \to \C^\times \to \C^\times \to 1\]
	is exact but
	\[1 \to\{\pm 1\} \to \R^\times \xrightarrow{x \mapsto x^2} \R^\times\]
	is not surjective on the right.
\end{example}

We have shown that the functor $M \to M^G$ is left exact.
% https://math.stackexchange.com/questions/1424102/relationship-between-galois-cohomology-and-etale-cohomology
\[H^1(\Gal(k),M) \cong H_\text{\et}^1(\Spec(k), \widetilde{M})\]

\begin{definition}
	Let $M$ be a $G$-module. The group of $1$-cochains from $G$ to $M$ is defined to be  $C^1(G, M) = \{\varphi: G \to M\}$
\end{definition}

\section{Hilbert's theorem 90}
Let $k$ be a field, $L$ a Galois extension of $k$ and $G = \Gal(L/k)$. A sieve s
