In Chapter 1, we fully described the \'etale site of $\Spec(k)$ for $k$ a field. We will now describe the category of sheaves of $\Et/\Spec(k)$.
Recall that a scheme $U$ is \'etale and of finite type over $k$ is a disjoint union $U = \coprod \Spec(L_i)$ where each $L_i$ is a separable field extension of $k$. Choosing a geometric point $\overline{x}$ of $\Spec(k)$ is equivalent to choosing a separable closure $k_s$ of $k$. Now the \'etale fundamental group $\pi_1^\et(X, \overline{x})$ equals the Galois group $\Gal(k) = \Gal(k_s, k)$.

By Theorem \ref{thm:sheaf_condition}, it suffices to show to show the sheaf condition for a single covering $\Spec(L) \to \Spec(L')$, where $L'/L/k$ are separable field extensions.

By Theorem \ref{thm:sheaf_condition}, presheaf $F$ on $\Et/k$ is a sheaf if and only if \ref{diagram:equalizer} is exact for a single affine cover $\Spec(A) \to \Spec(B)$, but affine \'etale covers in $\Et/k$ are precisely of the form $\coprod \Spec(L_i) \to \coprod \Spec$ where $L_i$ is separable over $k$, so the sheaf condition becomes

\[
	F(\Spec(L) \to \prod_{i} F(\Spec(L') \xbigtoto{} \prod_{i,j} F(\Spec(\Spec(L' \otimes_L L')
\]

\begin{enumerate}
	\item $F(\prod A_i) = \bigoplus F(A_i)$ for every finite family $\{A_i\}$ of \'etale algebra
	\item $F(L) \xrightarrow{\sim} F(K)^{\Gal(K/k)}$ for finite Galois extensions $K/L/k$
\end{enumerate}
For $F$ a sheaf on $\Et/k$ define $M_F = \varprojlim F(K)$, where the colimit runs over all finite Galois extensions over $k$. Then $M_F$ is a discrete $\Gal(k)$-module. Converseley, if $M$ is a discrete $G$-module, define $F_m(A) = \Hom_{\Gal(k)}(F(A),M)$, where $F(A) = \Hom(A, k_s)$. Then $F_M$ is a sheaf on $\Spec(k)$. This defines an equivalence of categories between the \'etale topos $\sh(\Et/k)$ of $k$ and the category of discrete $G$-modules.

\begin{construction}
	Let $G$ be a topological group. Denote by $BG$ the category of \textit{right $G$-sets} whose objects are sets $X$ equipped with a right $G$-action $X \times G \to X$ which is continuous when $X$ is given the discrete topology. Let $\Hom_G(X,Y)$ denote the set of morphisms in $BG$, which consists $G$-equivariant functions.
\end{construction}

\begin{theorem}
	Let $G$ be a topological group. Then the category of $G$-sets is equivalent to the topos of sheaves on the atomic site, whose objects are open subgroups of $G$ and morphisms $H \to K$ are the left cosets $aK$ such that $H \subseteq aKa^{-1}$.\\
	For a proof and definitions, see \cite{MacLane/Moerdijk:1994}, Chapter 3.9
\end{theorem}
